Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-11-19 paper/amia.tex
Auto Update from local Sharelatex

KFP addresses the issue of data access by generating data that is ``statistically similar'' to the real data but does not itself contain any sensitive data. We collectively refer to de-identified data and synthetic data as \emph{faux-data}. We use the term faux as it is used in the fashion sense of the word: the use of man made materials that look and feel like real leather, fur, etc., but without the problematic derivation from live animals and reliance upon limited resources. This faux-data can be analyzed, cleaned, feature-engineered, etc. as if it were the actual source data. KFP provides a standard mechanism for wrapping a privacy protection method into a plug-in which integrates the method with the Pandas DataFrame model. Two of these plug-ins are provided with full documentation for creating other plug-ins.

@@

KFP focuses on generating faux-data narrowed to a specific subset that a researcher is interested in rather than attempting to generate an entire population of data such as an entire EHR or longitudinal patient record. By focusing on just the data needed, performance is improved, the need for extensive modeling or metadata configuration is reduced, and the amount of faux-data generated and stored is minimized. Although the plugable methods included for faux-data generation have been shown to effectively replace source data for analysis, KFP facilitates a more through process that includes an initial exploration with faux-data followed by a repetition of methods on original source data through query logging and thereby aiding in replication.

@@

KFP provides a framework by which any number of methods for data privacy can be carried out. This framework is comprised of a some base classes and methods that can be extended or overridden, several examples of plugins, and unit tests for validation purposes. As of this writing we have implemented two plugins that use different techniques for data synthesis: a kernel density estimator and DataSynthesizer. The kernel density estimator from scipy.stats.gaussian\_kde uses the method developed by Silverman \cite{silverman_density_1986} which handles ordinal and ratio data yet runs quickly on standard consumer level hardware. Two methods for this plugin are provided: an independent attribute mode where each variable is considered in isolation, and a correlated attribute mode where all variables are evaluated and synthesized together on an observation by observation basis. The DataSynthesizer method, created by Ping et al. \cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data. As a result of their methods, the DataSynthesizer offers a unique contribution to the synthetic data generation space: it can work with no configuration other than input data, or can be configured to provide more custom results. In DataSynthesizer, the authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}).

@@

Table~\ref{timing_results} documents results obtained from running the various plugins. Source code for running these performance tests are available in the Jupyter notebook performance\_tests.ipynb. The "Trivial" method provides a baseline comparison for evaluating the overhead of Pandas and correct input/output of the plugin class and function overloading mechanism; it returns the input data frame unmodified. The KDE methods leveraging scipy.stats.gaussian\_kde act as an example of how to create plugins. Additionally the independent vs correlated KDE methods offer different accommodations for performance with correlated vs non-correlated source data. A couple of DataSynthesizer (abbreviated DS in the table) modes are used to demonstrate performance differences as well as generated synthetic data differences. "Independent" mode generates synthetic data with each attribute being modeled independently from the others. "Correlated" attribute mode finds inter-column relationships to more accurately generate synthetic data. Both DataSynthesizer modes are run with no configuration and again "w/Config" by passing in some column-wise dataset specific configuration.

@@

Fast generation of synthetic data is important in a self-service setting where researchers can generate their own data as needed. As shown in the results, some methods are significantly faster than others as dataset size increases. Another key desire is to have synthetic data be as close as possible to real data without compromising individual privacy. While the KDE plugin is a simple method, it quickly generates data that looks similar to the input data and works well for the range of data types used. DataSynthesizer in "Independent" mode is quick for the tested range of dataset sizes, but without additional configuration, it doesn't generate results that closely match the input dataset. As an example the "Code" column should contain valid International Statistical Classification of Diseases and Related Health Problems, Tenth Revision (ICD-10) codes, but instead has random strings that are similar in length to actual ICD-10 codes that do not line up with values in other columns. The DataSynthesizer "Correlated" attribute mode generates more realistic synthetic data than the "Independent" mode as variables in a single observation that are correlated are modeled together. The "Correlated" method does have a significant larger computational burden when generating synthetic data from larger input dataset sizes.

@@

KFP removes barriers to data access and data sharing via self-service faux-data generation. Users of KFP do not need to have access to a protected dataset nor does a human have to be involved in translating researchers data needs into a non-protected dataset. This self-service data can be differentially private or meet other privacy needs based on plugin capabilities. With faux-data, researchers can publicly share data upon which their research relies without organizational fear of privacy breaches. KFP also facilitates a process by which evaluation, analysis, or model building is first performed with faux-data followed by repetition upon private data.

>>>>

KFP addresses the issue of data access by generating data that is ``statistically similar'' to the real data but does not itself contain any sensitive data. We collectively refer to de-identified data and synthetic data as \emph{faux-data}. We use the term faux as it is used in the fashion sense of the word: the use of man made materials that look and feel like real leather, fur, etc., but without the problematic derivation from live animals and reliance upon limited resources. This faux-data can be analyzed, cleaned, feature-engineered, etc. as if it were the actual source data. KFP provides a standard mechanism for wrapping a privacy protection method into a plugin which integrates the method with the Pandas DataFrame model. Two of these plugins are provided with full documentation for creating other plugins.

@@

KFP focuses on generating faux-data narrowed to a specific subset that a researcher is interested in rather than attempting to generate an entire population of data such as an entire EHR or longitudinal patient record. By focusing on just the data needed, performance is improved, the need for extensive modeling or metadata configuration is reduced, and the amount of faux-data generated and stored is minimized. Although the plugin methods included for faux-data generation have been shown to effectively replace source data for analysis, KFP facilitates a more through process that includes an initial exploration with faux-data followed by a repetition of methods on original source data through query logging and thereby aiding in replication.

@@

KFP provides a framework by which any number of methods for data privacy can be carried out. This framework is comprised of base classes and methods that can be extended or overridden, several examples of plugins, and unit tests for validation purposes. As of this writing we have implemented two plugins that use different techniques for data synthesis: a kernel density estimator and DataSynthesizer. The kernel density estimator from scipy.stats.gaussian\_kde uses the method developed by Silverman \cite{silverman_density_1986} which handles ordinal and ratio data yet runs quickly on standard consumer level hardware. Two methods for this plugin are provided: an independent attribute mode where each variable is considered in isolation, and a correlated attribute mode where all variables are evaluated and synthesized together on an observation by observation basis. The DataSynthesizer method, created by Ping et al. \cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data. As a result of their methods, the DataSynthesizer offers a unique contribution to the synthetic data generation space: it can work with no configuration other than input data, or can be configured to provide more custom results. In DataSynthesizer, the authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}).

@@

Table~\ref{timing_results} documents results obtained from running the various plugins. Source code for running these performance tests are available in the Jupyter notebook performance\_tests.ipynb. The "Trivial" method provides a baseline comparison for evaluating the overhead of Pandas and correct input/output of the plugin class and function overloading mechanism; it returns the input data frame unmodified. The KDE methods leveraging scipy.stats.gaussian\_kde act as an example of how to create plugins. Additionally, the independent vs correlated KDE methods offer different accommodations for performance with correlated vs non-correlated source data. A couple of DataSynthesizer (abbreviated DS in the table) modes are used to demonstrate performance differences as well as generated synthetic data differences. "Independent" mode generates synthetic data with each attribute being modeled independently from the others. "Correlated" attribute mode finds inter-column relationships to more accurately generate synthetic data. Both DataSynthesizer modes are run with no configuration and again "w/Config" by passing in some column-wise dataset specific configuration.

@@

Fast generation of synthetic data is important in a self-service setting where researchers can generate their own data as needed. As shown in the results, some methods are significantly faster than others as dataset size increases. Another key desire is to have synthetic data be as close as possible to real data without compromising individual privacy. While the KDE plugin is a simple method, it quickly generates data that looks similar to the input data and works well for the range of data types used. DataSynthesizer in "Independent" mode is quick for the tested range of dataset sizes, but without additional configuration, it doesn't generate results that closely match the input dataset. As an example, the "Code" column should contain valid International Statistical Classification of Diseases and Related Health Problems, Tenth Revision (ICD-10) codes, but instead has random strings that are similar in length to actual ICD-10 codes that do not line up with values in other columns. The DataSynthesizer "Correlated" attribute mode generates more realistic synthetic data than the "Independent" mode as variables in a single observation that are correlated are modeled together. The "Correlated" method does have a significant larger computational burden when generating synthetic data from larger input dataset sizes.

@@

KFP removes barriers to data access and data sharing via self-service faux-data generation. Users of KFP do not need to have access to a protected dataset nor does a human have to be involved in translating researcher's data needs into a non-protected dataset. This self-service data can be differentially private or meet other privacy needs based on plugin capabilities. With faux-data, researchers can publicly share data upon which their research relies without organizational fear of privacy breaches. KFP also facilitates a process by which evaluation, analysis, or model building is first performed with faux-data followed by repetition upon private data.
